Evaluating Regularization

### 2019-05-16 Scripts/evaluating_feature_reduction.Rmd
added results scripts

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

@@

## Heatmaps of whether or not a variable was reduced

### GM12878

####10kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")

features <- names(train)[-1]
features <- features[grep("dist", features)]
features <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "Gm12878", 
                                                    "dist", 
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", features)

#None
##OC
enetcoefs_none_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_none_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_none_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/enetcoefs.rds")

#RUS
##OC
enetcoefs_RUS_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_RUS_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_RUS_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")

#ROS
##OC
enetcoefs_ROS_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_ROS_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_ROS_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")

#SMOTE
##OC
enetcoefs_SMOTE_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_SMOTE_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_SMOTE_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")

enetcoefslist <- list(enetcoefs_none_oc_10kb_gm12878, 
                      enetcoefs_none_op_10kb_gm12878, 
                      enetcoefs_none_dist_10kb_gm12878,
                      enetcoefs_RUS_oc_10kb_gm12878, 
                      enetcoefs_RUS_op_10kb_gm12878, 
                      enetcoefs_RUS_dist_10kb_gm12878,
                      enetcoefs_ROS_oc_10kb_gm12878, 
                      enetcoefs_ROS_op_10kb_gm12878, 
                      enetcoefs_ROS_dist_10kb_gm12878,
                      enetcoefs_SMOTE_oc_10kb_gm12878, 
                      enetcoefs_SMOTE_op_10kb_gm12878, 
                      enetcoefs_SMOTE_dist_10kb_gm12878)

enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})

featuremat_10kb_gm12878 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
                                                                    "Predictor Type"=rep(c("OC",
                                                                                         "OP", 
                                                                                         "Distance"),4)))

for(j in 1:length(enetcoefslist)){
    featuremat_10kb_gm12878[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
}

#using lattice
levelplot(t(featuremat_10kb_gm12878), 
          colorkey=FALSE, 
          scales=list(x=list(rot=45),
                      alternating=3), 
          col.regions=c("white", "red"),
          aspect="fill",panel = function(...){
            panel.levelplot(...)
            panel.abline(v = 3.5);
            panel.abline(v = 6.5);
            panel.abline(v = 9.5);
          },
          xlab="",
          ylab="")
grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))

@@

####25kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")

features <- names(train)[-1]
features <- features[grep("dist", features)]
features <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "Gm12878", 
                                                    "dist", 
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", features)

#None
##OC
enetcoefs_none_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_none_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_none_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/enetcoefs.rds")

#RUS
##OC
enetcoefs_RUS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_RUS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_RUS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")

#ROS
##OC
enetcoefs_ROS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_ROS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_ROS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")

#SMOTE
##OC
enetcoefs_SMOTE_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_SMOTE_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_SMOTE_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")

enetcoefslist <- list(enetcoefs_none_oc_25kb_gm12878, 
                      enetcoefs_none_op_25kb_gm12878, 
                      enetcoefs_none_dist_25kb_gm12878,
                      enetcoefs_RUS_oc_25kb_gm12878, 
                      enetcoefs_RUS_op_25kb_gm12878, 
                      enetcoefs_RUS_dist_25kb_gm12878,
                      enetcoefs_ROS_oc_25kb_gm12878, 
                      enetcoefs_ROS_op_25kb_gm12878, 
                      enetcoefs_ROS_dist_25kb_gm12878,
                      enetcoefs_SMOTE_oc_25kb_gm12878, 
                      enetcoefs_SMOTE_op_25kb_gm12878, 
                      enetcoefs_SMOTE_dist_25kb_gm12878)

enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})

featuremat_25kb_gm12878 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
                                                                    "Predictor Type"=rep(c("OC",
                                                                                         "OP", 
                                                                                         "Distance"),4)))

for(j in 1:length(enetcoefslist)){
    featuremat_25kb_gm12878[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
}

#using lattice
levelplot(t(featuremat_25kb_gm12878), 
          colorkey=FALSE, 
          scales=list(x=list(rot=45),
                      alternating=3), 
          col.regions=c("white", "red"),
          aspect="fill",panel = function(...){
            panel.levelplot(...)
            panel.abline(v = 3.5);
            panel.abline(v = 6.5);
            panel.abline(v = 9.5);
          },
          xlab="",
          ylab="")
grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))

####50kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")

features <- names(train)[-1]
features <- features[grep("dist", features)]
features <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "Gm12878", 
                                                    "dist", 
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", features)

#None
##OC
enetcoefs_none_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_none_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_none_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/enetcoefs.rds")

#RUS
##OC
enetcoefs_RUS_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_RUS_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_RUS_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")

#ROS
##OC
enetcoefs_ROS_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_ROS_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_ROS_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")

#SMOTE
##OC
enetcoefs_SMOTE_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_SMOTE_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_SMOTE_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")

enetcoefslist <- list(enetcoefs_none_oc_50kb_gm12878, 
                      enetcoefs_none_op_50kb_gm12878, 
                      enetcoefs_none_dist_50kb_gm12878,
                      enetcoefs_RUS_oc_50kb_gm12878, 
                      enetcoefs_RUS_op_50kb_gm12878, 
                      enetcoefs_RUS_dist_50kb_gm12878,
                      enetcoefs_ROS_oc_50kb_gm12878, 
                      enetcoefs_ROS_op_50kb_gm12878, 
                      enetcoefs_ROS_dist_50kb_gm12878,
                      enetcoefs_SMOTE_oc_50kb_gm12878, 
                      enetcoefs_SMOTE_op_50kb_gm12878, 
                      enetcoefs_SMOTE_dist_50kb_gm12878)

enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})

featuremat_50kb_gm12878 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
                                                                    "Predictor Type"=rep(c("OC",
                                                                                         "OP", 
                                                                                         "Distance"),4)))

for(j in 1:length(enetcoefslist)){
    featuremat_50kb_gm12878[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
}

#using lattice
levelplot(t(featuremat_50kb_gm12878), 
          colorkey=FALSE, 
          scales=list(x=list(rot=45),
                      alternating=3), 
          col.regions=c("white", "red"),
          aspect="fill",panel = function(...){
            panel.levelplot(...)
            panel.abline(v = 3.5);
            panel.abline(v = 6.5);
            panel.abline(v = 9.5);
          },
          xlab="",
          ylab="")
grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))

####100kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")

features <- names(train)[-1]
features <- features[grep("dist", features)]
features <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "Gm12878", 
                                                    "dist", 
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", features)

#None
##OC
enetcoefs_none_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_none_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_none_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/enetcoefs.rds")

#RUS
##OC
enetcoefs_RUS_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_RUS_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_RUS_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")

#ROS
##OC
enetcoefs_ROS_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_ROS_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_ROS_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")

#SMOTE
##OC
enetcoefs_SMOTE_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_SMOTE_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_SMOTE_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")

enetcoefslist <- list(enetcoefs_none_oc_100kb_gm12878, 
                      enetcoefs_none_op_100kb_gm12878, 
                      enetcoefs_none_dist_100kb_gm12878,
                      enetcoefs_RUS_oc_100kb_gm12878, 
                      enetcoefs_RUS_op_100kb_gm12878, 
                      enetcoefs_RUS_dist_100kb_gm12878,
                      enetcoefs_ROS_oc_100kb_gm12878, 
                      enetcoefs_ROS_op_100kb_gm12878, 
                      enetcoefs_ROS_dist_100kb_gm12878,
                      enetcoefs_SMOTE_oc_100kb_gm12878, 
                      enetcoefs_SMOTE_op_100kb_gm12878, 
                      enetcoefs_SMOTE_dist_100kb_gm12878)

enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})

featuremat_100kb_gm12878 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
                                                                    "Predictor Type"=rep(c("OC",
                                                                                         "OP", 
                                                                                         "Distance"),4)))

for(j in 1:length(enetcoefslist)){
    featuremat_100kb_gm12878[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
}

#using lattice
levelplot(t(featuremat_100kb_gm12878), 
          colorkey=FALSE, 
          scales=list(x=list(rot=45),
                      alternating=3), 
          col.regions=c("white", "red"),
          aspect="fill",panel = function(...){
            panel.levelplot(...)
            panel.abline(v = 3.5);
            panel.abline(v = 6.5);
            panel.abline(v = 9.5);
          },
          xlab="",
          ylab="")
grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))

####Combined

```{r}
all_featuremat_gm12878 <- cbind(featuremat_10kb_gm12878,
                                featuremat_25kb_gm12878,
                                featuremat_50kb_gm12878,
                                featuremat_100kb_gm12878)
all_featuremat_gm12878 <- all_featuremat_gm12878[,c(seq(1,48,3),
                                                    seq(2,48,3),
                                                    seq(3,48,3))]
colnames(all_featuremat_gm12878) <- rep(c("None", "RUS", "ROS", "SMOTE"), 12)

levelplot(t(all_featuremat_gm12878), 
          colorkey=FALSE, 
          scales=list(x=list(rot=45, cex=.5),
                      #alternating=3,
                      y=list(cex=.5)), 
          col.regions=c("white", "red"),
          aspect="fill",panel = function(...){
            panel.levelplot(...)
			#horizontal lines
			panel.abline(h = 1.5);
			panel.abline(h = 2.5);
			panel.abline(h = 3.5);
			panel.abline(h = 4.5);
			panel.abline(h = 5.5);
			panel.abline(h = 6.5);
			panel.abline(h = 7.5);
			panel.abline(h = 8.5);
			panel.abline(h = 9.5);
			panel.abline(h = 10.5);
			panel.abline(h = 11.5);
			panel.abline(h = 12.5);
			panel.abline(h = 13.5);
			panel.abline(h = 14.5);
			panel.abline(h = 15.5);
			panel.abline(h = 16.5);
			panel.abline(h = 17.5);
			panel.abline(h = 18.5);
			panel.abline(h = 19.5);
			panel.abline(h = 20.5);
			panel.abline(h = 21.5);
			panel.abline(h = 22.5);
			panel.abline(h = 23.5);
			panel.abline(h = 24.5);
			panel.abline(h = 25.5);
			panel.abline(h = 26.5);
			panel.abline(h = 27.5);
			panel.abline(h = 28.5);
			panel.abline(h = 29.5);
			panel.abline(h = 30.5);
			panel.abline(h = 31.5);
			panel.abline(h = 32.5);
			panel.abline(h = 33.5);
			panel.abline(h = 34.5);
			panel.abline(h = 35.5);
			panel.abline(h = 36.5);
			panel.abline(h = 37.5);
			panel.abline(h = 38.5);
			panel.abline(h = 39.5);
			panel.abline(h = 40.5);
			panel.abline(h = 41.5);
			panel.abline(h = 42.5);
			panel.abline(h = 43.5);
			panel.abline(h = 44.5);
			panel.abline(h = 45.5);
			panel.abline(h = 46.5);
			panel.abline(h = 47.5);
			panel.abline(h = 48.5);
			panel.abline(h = 49.5);
			panel.abline(h = 50.5);
			panel.abline(h = 50.5);
			panel.abline(h = 51.5);
			panel.abline(h = 52.5);
			panel.abline(h = 53.5);
			panel.abline(h = 54.5);
			panel.abline(h = 55.5);
			panel.abline(h = 56.5);
			panel.abline(h = 57.5);
			panel.abline(h = 58.5);
			panel.abline(h = 59.5);
			panel.abline(h = 60.5);
			panel.abline(h = 61.5);
			panel.abline(h = 62.5);
			panel.abline(h = 63.5);
			panel.abline(h = 64.5);
			panel.abline(h = 65.5);
			panel.abline(h = 66.5);
			panel.abline(h = 67.5);
			panel.abline(h = 68.5);
			panel.abline(h = 69.5);
			panel.abline(h = 70.5);
			panel.abline(h = 71.5);
			panel.abline(h = 72.5);
			panel.abline(h = 73.5);
			panel.abline(h = 74.5);
			panel.abline(h = 75.5);
			panel.abline(h = 76.5);
			panel.abline(h = 77.5);
			panel.abline(h = 78.5);
			panel.abline(h = 79.5);
			panel.abline(h = 80.5);
			panel.abline(h = 81.5);
			panel.abline(h = 82.5);
			panel.abline(h = 83.5);
			panel.abline(h = 84.5);
			panel.abline(h = 85.5);
			panel.abline(h = 86.5);
			panel.abline(h = 87.5);
			panel.abline(h = 88.5);
			panel.abline(h = 89.5);
			panel.abline(h = 90.5);
			panel.abline(h = 91.5);
			panel.abline(h = 92.5);
			panel.abline(h = 93.5);
			panel.abline(h = 94.5);
			panel.abline(h = 95.5);
			panel.abline(h = 96.5);
			panel.abline(h = 97.5);
			panel.abline(h = 98.5);
			panel.abline(h = 99.5);
			panel.abline(h = 100.5);
			panel.abline(h = 101.5);
			panel.abline(h = 102.5);
			panel.abline(h = 103.5);

			#vertical lines
            panel.abline(v = 1.5);
            panel.abline(v = 2.5);
            panel.abline(v = 3.5);
            panel.abline(v = 4.5);
            panel.abline(v = 5.5);
            panel.abline(v = 6.5);
            panel.abline(v = 7.5);
            panel.abline(v = 8.5);
            panel.abline(v = 9.5);
            panel.abline(v = 10.5);
            panel.abline(v = 11.5);
            panel.abline(v = 12.5);
            panel.abline(v = 13.5);
            panel.abline(v = 14.5);
            panel.abline(v = 15.5);
            panel.abline(v = 16.5, col="yellow");
            panel.abline(v = 17.5);
            panel.abline(v = 18.5);
            panel.abline(v = 19.5);
            panel.abline(v = 20.5);
            panel.abline(v = 21.5);
            panel.abline(v = 22.5);
            panel.abline(v = 23.5);
            panel.abline(v = 24.5);
            panel.abline(v = 25.5);
            panel.abline(v = 26.5);
            panel.abline(v = 27.5);
            panel.abline(v = 28.5);
            panel.abline(v = 29.5);
            panel.abline(v = 30.5);
            panel.abline(v = 31.5);
            panel.abline(v = 32.5, col="yellow");
            panel.abline(v = 33.5);
            panel.abline(v = 34.5);
            panel.abline(v = 35.5);
            panel.abline(v = 36.5);
            panel.abline(v = 37.5);
            panel.abline(v = 38.5);
            panel.abline(v = 39.5);
            panel.abline(v = 40.5);
            panel.abline(v = 41.5);
            panel.abline(v = 42.5);
            panel.abline(v = 43.5);
            panel.abline(v = 44.5);
            panel.abline(v = 45.5);
            panel.abline(v = 46.5);
            panel.abline(v = 47.5);
          },
          xlab="",
          ylab="")
```

### K562

####10kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")

features <- names(train)[-1]
features <- features[grep("dist", features)]
features <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "K562", 
                                                    "dist", 
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", features)

#None
##OC
enetcoefs_none_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_none_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_none_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/enetcoefs.rds")

#RUS
##OC
enetcoefs_RUS_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_RUS_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_RUS_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")

#ROS
##OC
enetcoefs_ROS_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_ROS_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_ROS_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")

#SMOTE
##OC
enetcoefs_SMOTE_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
##OP
enetcoefs_SMOTE_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
##Distance
enetcoefs_SMOTE_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")

enetcoefslist <- list(enetcoefs_none_oc_10kb_K562, 
                      enetcoefs_none_op_10kb_K562, 
                      enetcoefs_none_dist_10kb_K562,
                      enetcoefs_RUS_oc_10kb_K562, 
                      enetcoefs_RUS_op_10kb_K562, 
                      enetcoefs_RUS_dist_10kb_K562,
                      enetcoefs_ROS_oc_10kb_K562, 
                      enetcoefs_ROS_op_10kb_K562, 
                      enetcoefs_ROS_dist_10kb_K562,
                      enetcoefs_SMOTE_oc_10kb_K562, 
                      enetcoefs_SMOTE_op_10kb_K562, 
                      enetcoefs_SMOTE_dist_10kb_K562)

enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})

featuremat_10kb_k562 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
                                                                    "Predictor Type"=rep(c("OC",
                                                                                         "OP", 
                                                                                         "Distance"),4)))

for(j in 1:length(enetcoefslist)){
    featuremat_10kb_k562[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
}

>>>>

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

@@

##GM12878

```{r}
chromstates <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
chromstates <- chromstates[grep("Gm12878", chromstates)]
chromstates <- gsub(paste0(c("Gm12878-", ".bed"), collapse = "|"),"",chromstates)

histones <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
histones <- histones[grep("Gm12878", histones)]
histones <- gsub(paste0(c("Gm12878-", ".bed"), collapse = "|"),"",histones)

tfbs <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878")
tfbs <- gsub(paste0(c("Gm12878-", ".bed", "-Haib", "-Sydh", "-Broad", "-Uw", "-Uta", "-Chicago"), collapse = "|"),"", tfbs)
tfbs <- tfbs[!duplicated(tfbs)]

ratio.per.chr <- as.numeric()

for(i in c("10kb", "25kb", "50kb", "100kb")){
  for(j in paste0("CHR", c(1:8,10:22))){
    enetvars <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/",
                                 i,
                                 "/results_by_chr/",
                                 j,
                                 "/smote/distance/enet/enetcoefs.rds"))

    enetvars <- gsub("_dist", "", enetvars)

    cssratio <- length(intersect(enetvars, chromstates))/length(chromstates)
    hmratio <- length(intersect(enetvars, histones))/length(histones)
    tfbsratio <- length(intersect(enetvars, tfbs))/length(tfbs)

    #res.per.chr <- c(res.per.chr, i)
    #ann.per.chr <- c(ann.per.chr, j)
    #chr.per.chr <- c(chr.per.chr, c("CSS", "HM", "TFBS"))
    ratio.per.chr <- c(ratio.per.chr, c(cssratio,hmratio,tfbsratio))

  }
}

enet_ratios_gm12878 <- cbind.data.frame(Ratio=ratio.per.chr,
                                        Annotation=rep(c("CSS","HM","TFBS"), 84),
                                        Chromosome=rep(c(rep("CHR1",3),
                                                     rep("CHR2",3),
                                                     rep("CHR3",3),
                                                     rep("CHR4",3),
                                                     rep("CHR5",3),
                                                     rep("CHR6",3),
                                                     rep("CHR7",3),
                                                     rep("CHR8",3),
                                                     rep("CHR10",3),
                                                     rep("CHR11",3),
                                                     rep("CHR12",3),
                                                     rep("CHR13",3),
                                                     rep("CHR14",3),
                                                     rep("CHR15",3),
                                                     rep("CHR16",3),
                                                     rep("CHR17",3),
                                                     rep("CHR18",3),
                                                     rep("CHR19",3),
                                                     rep("CHR20",3),
                                                     rep("CHR21",3),
                                                     rep("CHR22",3)),4),
                                        Resolution=c(rep("10 kb", 21*3),
                                                     rep("25 kb", 21*3),
                                                     rep("50 kb", 21*3),
                                                     rep("100 kb", 21*3)))

enet_ratios_gm12878_summ <- enet_ratios_gm12878 %>%
  group_by(Resolution, Annotation) %>%
  dplyr::summarise(AveRatio = mean(Ratio, na.rm = TRUE),
            AveRatioSD = sd(Ratio, na.rm = TRUE))

@@
